\sectionTitle{EXPERIENCE}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
\experience
    {2023 - now}{Buisness Analyst}{intive}{}
    {} {
        \begin{itemize}
            \item Supporting Product Owner in delivering a new e-commerce platform for a multinational chain of stores.
            \item Defining requirements by identifying project milestones, phases, and elements.
            \item Analysing and communicating the impact of functionality changes on project cost and schedule.
            \item Transforming designs, architectural diagrams, and client needs into clear and testable user stories.
        \end{itemize}
        } {\sc requirement analysis, \sc less, \sc process improvement, \sc relationship building, \sc big picture thinking}
\emptySeparator
\experience
    {2023 - now}{Buisness Analyst}{intive}{}
    {} {
        \begin{itemize}
            \item Test leader for a team of nine, for a User Administration part of a VOD application.
            \item Managing test processes, best practices, workflows, and priorities.
            \item Providing training for new team members.
            \item Exploratory, feature, accessibility, and regression testing.
            \item Creating Test Cases and basic automation tests, based on impact analysis.
        \end{itemize}
        } {\sc leadership, \sc test case, \sc testrail, \sc accessibility, \sc testcafe, \sc sonic studio, \sc browserstack}
\emptySeparator
\experience
    {2019 - 2020}{Software Tester}{Vonage}{}
    {} {
        \begin{itemize}
            \item Member of Scrum team responsible for multiple microservices in complex call centre platform.
            \item Participating in the entire Software Development Life Cycle, from requirements analysis to maintaining customer satisfaction after product shipment.
            % \item Introducing a norm to ensure consistency in the release process for UI microservices across the company.
            \item Performing the role of Scrum Master for one team for a year.
            \item Member of the Recruitment team -- evaluating assignments and conducting interviews. 
        \end{itemize}
        } {\sc example mapping, \sc requirements analysis, \sc swagger, \sc scrum master, \sc postman, \sc recruitment}
\emptySeparator
\experience
    {2017 - 2018}   {Software Tester}{Bright IT}{}
    {} {
        \begin{itemize}
            \item Testing newly developed components in various CMS applications.
       \end{itemize}
        } {\sc sketch, \sc exploratory testing, \sc UX, \sc regression testing, \sc episerver, \sc magnolia, \sc teamSite, \sc estudio}
\emptySeparator
\experience
    {2016 - 2017}   {Software Tester}{Fingo}{}
    {} {
        \begin{itemize}
            \item Testing and supporting applications from financial reporting, regulation, and supervision area.
        \end{itemize}
        } {\sc xbrl, \sc customer support, \sc regression testing, \sc exploratory testing, \sc black-box testing, \sc sql, \sc regex}
\end{experiences}